\section{Experience}
\begin{tabularx}{
    \textwidth-0.4 cm-0.13cm
}{
    K{0.2 cm}
    R{4.1 cm}
}
    \textbf{Apple Computer}, Software Engineer, Intern
    \vspace{0.10 cm}
    \begin{highlights}
        \item Reduced time to render the user's buddy list by 75\% by implementing a prediction algorithm.
        \item Implemented iChat integration with OS X Spotlight Search by creating a tool that extracts metadata from saved chat transcripts and provides metadata to a system-wide search database.
        \item Redesigned chat file format and implemented backward compatibility for search.
    \end{highlights}
    &
    CA, USA
    June 2004 to Aug. 2004
    2 months
\end{tabularx}

\vspace{0.2 cm}
\begin{tabularx}{
    \textwidth-0.4 cm-0.13cm
}{
    K{0.2 cm}
    R{4.1 cm}
}
    \textbf{Microsoft Corporation}, Lead Student Ambassador

    \vspace{0.10 cm}

    \begin{highlights}
        \item Promoted to Lead Student Ambassador in the Fall of 2004, supervised 10 - 15 Student Ambassadors.
        \item Created and taught a computer science course, CSE 099: Software Design and Development.
    \end{highlights}
    &
    WA, USA

    Sept. 2003 to Apr. 2005

    1 year 7 months
\end{tabularx}

\vspace{0.2 cm}
\begin{tabularx}{
    \textwidth-0.4 cm-0.13cm
}{
    K{0.2 cm}
    R{4.1 cm}
}
    \textbf{University of Pennsylvania}, Head Teaching Assistant

    \vspace{0.10 cm}

    \begin{highlights}
        \item Implemented a user interface for the VS open file switcher (ctrl-tab) and extended it to tool windows.
        \item Created a service to provide gradient across VS and VS add-ins. Optimized service via caching.
        \item Programmer Productivity Research Center (Summers 2001, 2002)
        \item Built app to compute the similarity of all methods in a code base, reduced time from $\mathcal{O}(n^2)$ to $\mathcal{O}(n \log n)$. 
        \item Created a test case generation tool that creates random XML docs from XML Schema.
    \end{highlights}
    &
    PA, USA

    Oct. 2001 to May 2005

    3 years 7 months
\end{tabularx}

\vspace{0.2 cm}
\begin{tabularx}{
    \textwidth-0.4 cm-0.13cm
}{
    K{0.2 cm}
    R{4.1 cm}
}
    \textbf{Microsoft Corporation}, Software Design Engineer, Intern

    \vspace{0.10 cm}

    \begin{highlights}
        \item Promoted to Lead Student Ambassador in the Fall of 2004, supervised 10 - 15 Student Ambassadors.
    \end{highlights}
    &
    WA, USA

    June 2003 to Aug. 2003

    2 months
\end{tabularx}



\section{Publications}

\begin{tabularx}{\textwidth-0.4 cm-0.13cm}{K{0.2 cm} R{4.1 cm}}
    \textbf{Magneto-Thermal Thin Shell Approximation for 3D Finite Element Analysis of No-Insulation Coils}

    \vspace{0.10 cm}

    \mbox{A. Smith}, \mbox{\textbf{\textit{J. Doe}}}, \mbox{J. Derry}, \mbox{H. Tom}, \mbox{A. Andsurname}

    \vspace{0.10 cm}

    \href{https://doi.org/10.1109/TASC.2023.3340648}{10.1109/TASC.2023.3340648} ()    &
    Jan. 2004
\end{tabularx}

\section{Projects}
\begin{tabularx}{
    \textwidth-0.4 cm-0.13cm
}{
    K{0.2 cm}
    R{4.1 cm}
}
    \textbf{Multi-User Drawing Tool}

    \vspace{0.10 cm}

    \begin{highlights}
        \item Developed an electronic classroom where multiple users can view and simultaneously draw on a "chalkboard" with each person's edits synchronized.
        \item Used C++ and MFC.
    \end{highlights}
    &
    

    Jan. 2004
\end{tabularx}


\vspace{0.2 cm}
\begin{tabularx}{
    \textwidth-0.4 cm-0.13cm
}{
    K{0.2 cm}
    R{4.1 cm}
}
    \textbf{Synchronized Calendar}

    \vspace{0.10 cm}

    \begin{highlights}
        \item Developed a desktop calendar with globally shared and synchronized calendars, allowing users to schedule meetings with other users.
        \item Used C\#.NET, SQL, and XML.
    \end{highlights}
    &
    

    2003 to 2004
\end{tabularx}


\vspace{0.2 cm}
\begin{tabularx}{
    \textwidth-0.4 cm-0.13cm
}{
    K{0.2 cm}
    R{4.1 cm}
}
    \textbf{Operating System}

    \vspace{0.10 cm}

    \begin{highlights}
        \item Developed a UNIX-style OS with a scheduler, file system, text editor, and calculator.
        \item Used C.
    \end{highlights}
    &
    

    Jan. 2002
\end{tabularx}




\section{Additional Experience And Awards}

\begingroup\leftskip=0.2 cm
\advance\csname @rightskip\endcsname 0.2 cm
\advance\rightskip 0.2 cm

\textbf{Instructor (2003 - 2005):} Taught two full-credit Computer Science courses. \par\endgroup

\vspace{0.2 cm}
\begingroup\leftskip=0.2 cm
\advance\csname @rightskip\endcsname 0.2 cm
\advance\rightskip 0.2 cm

\textbf{Third Prize, Senior Design Projects:} Awarded 3rd prize for a synchronized calendar project out of 100 projects. \par\endgroup



\section{Technologies}

\begingroup\leftskip=0.2 cm
\advance\csname @rightskip\endcsname 0.2 cm
\advance\rightskip 0.2 cm

\textbf{Languages:} C++, C, Java, Objective-C, C\#.NET, SQL, JavaScript \par\endgroup

\vspace{0.2 cm}
\begingroup\leftskip=0.2 cm
\advance\csname @rightskip\endcsname 0.2 cm
\advance\rightskip 0.2 cm

\textbf{Software:} Visual Studio, Microsoft SQL Server, Eclipse, XCode, Interface Builder \par\endgroup




\mbox{\hrefWithoutArrow{https://yourwebsite.com/}{{\small\faLink}\hspace*{0.13cm}yourwebsite.com}}
\hspace*{0.5 cm}
\mbox{\hrefWithoutArrow{https://linkedin.com/in/yourusername}{{\small\faLinkedinIn}\hspace*{0.13cm}yourusername}}
\hspace*{0.5 cm}
\mbox{\hrefWithoutArrow{https://github.com/yourusername}{{\small\faGithub}\hspace*{0.13cm}yourusername}}
\hspace*{0.5 cm}